% Paper submitted to EMSOFT 2015 on Scalable Green Scheduling
%
% Authors: Truong X. Nghiem, Rahul Mangharam

\documentclass{sig-alternate}

\input{preamble}
\graphicspath{{figs/}}

% Some convenient commands
\newcommand{\XSet}{\ensuremath{\mathcal{X}}}
\newcommand{\WSet}{\ensuremath{\mathcal{W}}}
\newcommand{\ESet}{\ensuremath{\mathcal{E}}}
\newcommand{\VSet}{\ensuremath{\mathcal{V}}}
\newcommand{\SSet}{\ensuremath{\mathcal{S}}}
\newcommand{\RSet}{\ensuremath{\mathcal{R}}}
\newcommand{\PSet}{\ensuremath{\mathcal{P}}}
\newcommand{\ZSet}{\ensuremath{\mathcal{Z}}}
\newcommand{\Zero}{\ensuremath{\mathbf{0}}}
\newcommand{\One}{\ensuremath{\mathbf{1}}}
\newcommand{\IdentityMatrix}{\ensuremath{\mathbbm I}}

\begin{document}
%
% --- Author Metadata here ---
%\conferenceinfo{EMSOFT}{'97 El Paso, Texas USA}
%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
% --- End of Author Metadata ---

\title{Scalable Scheduling of Energy Control Systems} % Scalable Green Scheduling}
%\subtitle{[Extended Abstract]
%\titlenote{A full version of this paper is available at...}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

% \numberofauthors{2}
% %
% \author{
% % You can go ahead and credit any number of authors here,
% % e.g. one 'row of three' or two rows (consisting of one row of three
% % and a second row of one, two or three).
% %
% % The command \alignauthor (no curly braces needed) should
% % precede each author name, affiliation/snail-mail address and
% % e-mail address. Additionally, tag each line of
% % affiliation/address with \affaddr, and tag the
% % e-mail address with \email.
% %
% % 1st. author
% \alignauthor
% Truong X. Nghiem\\
%        \affaddr{Automatic Control Laboratory}\\
%        \affaddr{\'Ecole Polytechnique F\'ed\'erale de Lausanne}\\
%        \affaddr{Lausanne, Switzerland}\\
%        \email{xuan.nghiem@epfl.ch}
% % 2nd. author
% \alignauthor
% Rahul Mangharam\\
%        \affaddr{Dept. of Electrical \& Systems Engineering}\\
%        \affaddr{University of Pennsylvania}\\
%        \affaddr{Philadelphia, Pennsylvania, USA}\\
%        \email{rahulm@seas.upenn.edu}
% %\and  % use '\and' if you need 'another row' of author names
% % There's nothing stopping you putting the seventh, eighth, etc.
% % author on the opening page (as the 'third row') but we ask,
% % for aesthetic reasons that you place these 'additional authors'
% % in the \additional authors block, viz.
% % \additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
% % email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
% % (The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
% % \date{30 July 1999}
% % Just remember to make sure that the TOTAL number of authors
% % is the number that will appear on the first page PLUS the
% % number that will appear in the \additionalauthors section.
% }

\maketitle

%\simplenote{FOR THE TITLE: because we will not perform large scale simulations, we should not include ``large scale'' in the title. The followings are some keywords, in addition to ``green scheduling,'' that may be used in the title: scalable, embedded, simulation relation, hierarchical, hierarchical design, multi-level, input bound tracking.}

\begin{abstract}
  \simplenote{The abstract will be revised. Currently it doesn't reflect the actual contents.}

  This technical note presents new results of green scheduling for peak demand
  reduction in large-scale systems. What makes the green scheduling problem
  particularly hard is that its control variables are binary. The complexity
  grows exponentially with the scale of the system, making it impossible to
  handle systems with more than a few dozens variables, unless the simple
  periodic scheduling algorithm is used. While simple and scalable, periodic
  schedules are static and limited in their capability to handle dynamics,
  safety constraints, and disturbances.
  
  The new results presented here novelly combine techniques from control
  theory and computer science to solve the green scheduling problem for
  large-scale systems with hundreds or thousands subsystems. The original
  system with binary control variables are approximated by an {\emph{averaged
  system}} whose inputs are the {\emph{utilization values}} of the binary
  inputs within a given period. The error between the two systems can be
  bounded, which allows us to derive a safety constraint for the averaged
  system so that the original system's safety is guaranteed. This relaxation
  already reduces the green scheduling mixed integer program to a standard
  program with real variables. However, for a large-scale system over a long
  prediction horizon, the number of optimization variables can be
  prohibitively large, which not only affects the computation performance but
  also requires commercial optimization solvers and powerful computing
  hardware. To alleviate this issue, we abstract the averaged system by a
  simple scalar dynamical system whose control input is the total demand of
  all the subsystems. This model abstraction is achieved by extending the
  notion of simulation relations between transition systems to allow for input
  constraints between the systems. We develop conditions to test for
  simulation relations as well as algorithms to compute such a model
  abstraction. As a consequence, we only need to solve a small linear program
  to compute an optimal trace of the total demand. The total demand is then
  broken down, by solving a linear program much smaller than the original
  program, to individual utilization values of the subsystems in an interval.
  The actual schedule in each interval is then obtained by a low-level
  scheduling algorithm. We propose two such algorithms: a simple ad-hoc
  algorithm that may switch on and off a subsystem multiple times, and a
  2-dimensional packing algorithm that only switches any subsystem at most
  once in each interval.
  
  Numerical simulations in Matlab show the effectiveness and scalability of
  our approach.
\end{abstract}

% A category with the (minimum) three required fields
\category{H.4}{Information Systems Applications}{Miscellaneous}
%A category including the fourth, optional field follows...
\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]

\terms{Theory}

\keywords{ACM proceedings, \LaTeX, text tagging}

\input{intro}

\input{problem}

\input{overview}

\input{averaged}

\input{abstraction}

\input{abstractiongs}

\input{summary}

\input{simulation}

\input{conclusions}

%ACKNOWLEDGMENTS are optional
%\section{Acknowledgments}


%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{IEEEabrv,references}
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!


%APPENDICES are optional
%\balancecolumns
\appendix

% All the proofs
\input{proofs}

%\balancecolumns

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
