\section{Introduction}
\label{sec:intro}

Peak power consumption is a universal problem across energy control systems in electrical grids, buildings, electric vehicles and industrial automation where the uncoordinated operation of multiple controllers result in  temporally correlated electricity demand surges. For example, in the case of the electrical grid, when the popular UK TV soap Eastenders comes to an end five times a week, the grid has to deal with around 1.75 million kettles requiring power at the same time (to prepare tea). That is an additional \emph{3 gigawatts} of power for the roughly 3-5 minutes it takes each kettle to boil. So big is the surge, caused by correlated human behavior, that backup power stations have to go on standby across the country, and there is even additional power made available in France just in case the UK grid cannot cope~\cite{tvpickup}. 

In the case of building systems such as heating, ventilating, air conditioning and refrigeration (HVAC\&R) systems, chiller systems, and lighting systems operate independently of each other and frequently trigger concurrently, resulting in peak power demand. Most commercial buildings are subject to peak demand pricing which can be 200-400 times that of the nominal power rate~\cite{trfpeco}. High peak loads also lead to a higher cost of production and distribution of electricity and lower reliability. Therefore, peaks in electricity usage are inefficient and expensive for both suppliers and customers.

% In the case of electric and hybrid-electric vehicles, peak power consumption due to vehicle acceleration or hilly terrain results in a high current draw from the battery~\cite{battery}. This increases the operating temperature which reduces the battery lifetime and capacity and requires additional resources for cooling. Effectively managing hybrid energy sources to minimize peak power is an open research issue for electric vehicles with fast dynamics and limited load forecasts~\cite{hybrid}.

While there exist several different approaches to balance power consumption by load shifting and load shedding, they operate on coarse grained time scales and do not help in de-correlating energy sinks.
Several approaches, for instance \cite{sou2011scheduling,zhang2011optimal}, employed mixed integer optimization to find optimal schedules for electric loads.
Because mixed integer programming suffers a scalability issue when the number of integer/binary variables is large, these approaches often worked on coarse grained time scales to reduce the computational burden.
However, their run-time implementations still required powerful computer hardware and commercial optimization software.

While traditional real-time scheduling algorithms~\cite{realtimesys} may be applied to such resource sharing problems, they impose stringent constraints on the task model.
Generally, real-time scheduling is restricted to tasks whose worst case execution times are fixed and known a priori~\cite{rts}.
While this simplifies the runtime complexity, %for control systems
it does not effectively capture a control system's behavior whose operation is dependent on the plant dynamics and environmental conditions. 

The focus of this paper is on a scalable approach for fine-grained scheduling of energy control systems within an aggregate peak power envelop while ensuring the individual systems are maintained within the desired states.
Our main contributions are:
\begin{enumerate}
\item We developed a model abstraction method based on the concept of simulation relations between transition systems \cite{aluretal00dah,girardetal07amd}.  The method allows us to reduce the original multi-state multi-binary-input model to a single-state single-real-input model with input bound tracking and safety guarantees.
\item We developed a scalable hierarchical control structure based on the derived model abstraction.  The run-time controller involves only two small-scale linear programs and has a low computational requirement that it is potentially suitable for embedded platforms.  
\item Using simulations, we showed that while the mixed integer programming approach \cite{sou2011scheduling,zhang2011optimal} may not work beyond a trivially small-scale system, our approach can handle efficiently a much larger system with a fast sampling rate and a long control horizon.
\end{enumerate}
 

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "emsoft15gs"
%%% End:
